Clustering time series based on probability distributions across temporal granularities

### 2021-11-17 main.Rmd
Fig 7 and 8 updated

Determining the number of clusters is typically a difficult task. Many metrics have been defined for choosing clusters. Most metrics for choosing the optimal number of clusters, are based on comparing distances between observations within a class to those distances between observations between classes, which makes the assumption that there are some separated clusters. Some common procedures include the gap statistic [@tibshirani2001estimating], average silhouette width [@rousseeuw1987silhouettes], Dunn index [@dunn1973fuzzy] and the separation index ($sindex$) [@Hennig2019-eq; @Hennig2014-ah]. These are constructed by balancing within-cluster homogeneity and between-cluster separation.

@@

@@

```{r opt-cluster-tsne-jsd, fig.cap = "Clustering summaries: t-SNE computed on the $24$ selected customers (a), and separation index ($sindex$) for 2-10 clusters using JS (b) and WPD (c). Various choices in number of clusters would be recommended. Four clusters are visible in t-SNE, although it might hide a fifth cluster because dimension reduction to 2D may be insufficient to see the difference. JS suggests 3 and wpd suggests 3 or 6."}
#include_graphics("figs/opt_clust_parenthesis.png")
```

>>>>

Determining the number of clusters is typically a difficult task. Many metrics have been defined for choosing clusters. Most metrics for choosing the optimal number of clusters, are based on comparing distances between observations within a class to those distances between observations between classes, which makes the assumption that there are some separated clusters. Some common procedures include the gap statistic [@tibshirani2001estimating], average silhouette width [@rousseeuw1987silhouettes], Dunn index [@Dunn1973-gk] and the separation index ($sindex$) [@Hennig2019-eq; @Hennig2014-ah]. These are constructed by balancing within-cluster homogeneity and between-cluster separation.

@@

```{r all-data-rs}

```{r clustering-rs}

```{r opt-clusters-jsd-rs}

```{r opt-clusters-all}

@@

```{r opt-cluster-tsne-jsd, fig.cap = "Clustering summaries: t-SNE computed on the $24$ selected customers (a), and separation index ($sindex$) for $2$-$10$ clusters using JS-NQT, JS-RS and WPD in (b). Various choices in number of clusters would be recommended. Four clusters are visible in t-SNE, although it might hide a fifth cluster because dimension reduction to 2D may be insufficient to see the difference. JS-NQT suggests $3$, JS-RS suggests $3$ or $5$ and WPD suggests $3$ or $6$."}
#include_graphics("figs/opt_clust_parenthesis.png")
```
